Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-06 lloveras_2020_v2.tex
ediciones gramaticales y typos en V2.tex

{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}). In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

@@

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Firstly, the fast dynamics that typically characterizes those structures is absent from the data. Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the {DEMT technique} we refer the reader to \citet{frazin_2009}.}

@@

{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}. {In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}. This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.

The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$). In reality, the thin {transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients in a global model would require excessive numerical resources. As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.  To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.  At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}

@@

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations. The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}

{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}. The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.

@@

At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). As a result, for each field line one data point per tomographic cell {is obtained. This approach} was first used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}. For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

@@

\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $a\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.

In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height. This choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution.

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported the presence of down loops. As speculated by the authors of those works, down loops can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}

{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$. {To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {not} good enough, are {excluded from the} analysis. {The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. {The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The confidence level of both the exponential and linear fits must be larger than 90\%.} 
\end{enumerate}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}

@@

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

{The high temperature of the corona requires heating mechanisms to compensate for the energy losses. While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions. In particular, \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to maintain stability. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model{, detailed in Section \ref{awsom}.}

@@

{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry. Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}. {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}

@@

Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that in most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below in this section.

@@

{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs. We will return to this point in the conclusion section.}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&66 &(\Mi&\edit{21}\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&\edit{17}\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

{Table \ref{tabla_demt} summarizes a} quantitative comparative analysis between the results of the two {target rotations}. For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are expressed relative to the corresponding results for CR-2082.

@@

In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} To quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 10-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}

{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop). {For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}

{For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are characterized by {the largest} values of electron density. Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterized by {values of temperature that are progressively larger and farther} from the value $\Tc$, for both rotations.}

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is likely due to measurement errors. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}

@@

{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}. The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT. The following major results can be drawn.}

>>>>

{Combining the DEMT and AWSoM models, we carry out a detailed \edit{quantitative} analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}). In the case of CR-2208, the DEMT analysis is based \edit{on} data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

@@

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Firstly, the fast dynamics that typically characterizes those structures is \edit{absent/reduced} from the data. Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}

@@

\noindent 
{being the} \edit{average absolute relative difference} between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the {DEMT technique} we refer the reader to \citet{frazin_2009}.}

@@

{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}. {In its present version, the \edit{energy partitioning is improved}} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}. This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.

The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$). In reality, the thin {transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients in a global model would require excessive numerical resources. As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially \edit{broadened} to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.  To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K\edit{, where the subscripts represents electrons and ions}. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.  At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}

@@

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations. The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$}\edit{, where $L_{\perp}$ is transverse to the magnetic field direction.}

{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}. \del{The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun)} \edit{The spherical grid has an adaptive grid that has fine resolution near the Sun, and increases outward} with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range. The solar corona component uses about 3 million cells on $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. \edit{The AWSoM simulation of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT in the results section.}

@@

At this {stage, DEMT and AWSoM products} \edit{are} traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). As a result, for each field line one data point per tomographic cell {is obtained. This approach} was first used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}. \edit{For DEMT the data points used are} $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used \edit{are} $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

@@

\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $a\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $a$ estimates the radial gradient of the electron temperature along the loop, which we denote as $a = \dr\Tm$ hereafter, \edit{with} $\dr\equiv\er\cdot\nabla$ \edit{being} the radial derivative operator \edit{and} $\er$ is the heliocentric radial unit vector.

In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height. This choice of function provides a straightforward means to directly \edit{compare the observed} coronal thermodynamical state with the hydrostatic solution.

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported the presence of down loops. As speculated by the authors of those works, down loops can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}

{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$. We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$. {To test the goodness of the fit \del{to the temperature-height data} we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is \edit{weak}, are {excluded from the} analysis. {The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. {The chi-squared test to evaluate the quality of the \edit{fit} considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, \edit{a selected leg must meet three conditions:}

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height points must meet} $|\rhoTr| > 0.5$.
\item 
{The confidence level of both the exponential and linear fits must be larger than 90\%.} 
\end{enumerate}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types:}

@@

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type \edit{type 0 to II allows a study of the streamer belt in three distinct layers at increasing height.}}

@@

{The high temperature of the corona requires heating mechanisms to compensate for the energy losses. While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions. In particular, \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to maintain stability. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, as described in Section \ref{trace}.}

@@

Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model{, detailed in Section \ref{awsom}.}

@@

{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry. Rotation CR-2082} \edit{has} two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  {(not identified in the NOAA catalog)}. {Rotation CR-2208} \edit{has} two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ {(NOAA 12722, 12721)}.}

@@

Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic} and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below in this section.

@@

{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs. We will return to this point in the \edit{Conclusions}.}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&66 &(\Mi&\edit{21}\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&\edit{17}\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are \edit{given} as a percentual variation relative to the CR-2082 value \edit{in the parentheses.}}
\label{tabla_demt}
\end{table}

Table \ref{tabla_demt} summarizes \edit{the results of the quantitative comparative analysis between the two {target rotations}}. For CR-2082 quantities are expressed as absolute values, {while} for CR-2208 they are expressed relative to the corresponding results for CR-2082.

@@

In comparing the DEMT results obtained for the two selected targets, {we highlight} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} To quantify the systematic difference of the DEMT products {due to the different filter sets of} both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density {products are} essentially equal, the temperature \edit{based on AIA data} is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering \edit{this error}, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 10-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}

{To analyse the loop-integrated energy flux quantities introduced in Section \ref{trace}, we selected closed loops for which both legs have the same sign of the radial gradient of the electron temperature $\dr\Tm$.} In this way, according to the classification of both its legs, each loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop). {For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively.}

{For both rotations, the value of the {loop-integrated} radiative power $E_r$, measured by the quantity $\phi_r$, is largest for loops of type 0. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors contributing to maximize $E_r$ for loops of type 0. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0 are \edit{characterised} by {the largest} values of electron density. Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are \edit{characterised by temperatures that are are progressively larger, and farther from $\Tc$, for both rotations.}}

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}

@@

{For the two target rotations, Table \ref{tabla_comp} summarizes a quantitative comparative analysis between the results of the DEMT and AWSoM models {based on the results shown in Figures \ref{histos_2082} and \ref{histos_2208}}. The DEMT results are expressed as absolute values, while the ASWSoM results are informed as a percentual variation relative to the corresponding result for DEMT. \del{The following major results can be drawn.}}
